Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-09-07 awipev-CO2.Rmd
minor issue with plot profile

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if (!require("robfilter")) install.packages("robfilter")
if (!require("robfilter")) install.packages("robfilter")
library("robfilter")
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("reshape2")) install.packages("reshape2")
library("reshape2")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("lmtest")) install.packages("lmtest")
library("lmtest")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("seismicRoll")) install.packages("seismicRoll")
library("seismicRoll")
if (!require("scales")) install.packages("scales")
library("scales")
if (!require("cowplot")) install.packages("cowplot")
library(cowplot)
if (!require("htmlwidgets")) install.packages("htmlwidgets")
library("htmlwidgets")
if (!require("hms")) install.packages("hms")
library("hms")
if (!require("ragg")) install.packages("hms")
library("ragg")
if (!require("skimr")) install.packages("skimr")
library("skimr")

@@

plt <- sal_median %>%
  ggplot(aes(
    x = montht,
    y = as.factor(depth),
    fill = median(sal_insitu_ctd)
  ), color = "white") +
  geom_tile() +
  scale_fill_gradientn(colors = viridis(5), breaks = seq(31, 36, by = 1), na.value = "grey") +
  labs(x = "", y = "", fill = "Salinity") +
  scale_x_discrete(position = "top") +
  scale_y_discrete(name = "", limits = rev(levels(as.factor(tmp$depth)))) +
  # scale_y_discrete(name = "", limits = rev(levels(as.factor(tmp$depth))),
  #                  rev(levels(tmp$depth))[c(1,3,5,7,9)]) +
  # coord_equal() +
  theme(legend.position = "top",
        axis.text.y = element_text(size = 13),
        axis.text.x = element_text(size = 13),
        legend.text = element_text(size = 13),
        legend.title = element_text(size = 14),
        #legend.key.size = unit(1.5, "cm"),
        legend.key.height = unit(0.8, "cm"),
        legend.key.width  = unit(2, "cm"))
plt

>>>>

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
if (!require("tidyverse")) install.packages("tidyverse")
library(dplyr)
library(tidyverse)
if (!require("robfilter")) install.packages("robfilter")
if (!require("robfilter")) install.packages("robfilter")
library("robfilter")
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("reshape2")) install.packages("reshape2")
library("reshape2")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("lmtest")) install.packages("lmtest")
library("lmtest")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("seismicRoll")) install.packages("seismicRoll")
library("seismicRoll")
if (!require("scales")) install.packages("scales")
library("scales")
if (!require("cowplot")) install.packages("cowplot")
library(cowplot)
if (!require("htmlwidgets")) install.packages("htmlwidgets")
library("htmlwidgets")
if (!require("hms")) install.packages("hms")
library("hms")
if (!require("ragg")) install.packages("hms")
library("ragg")
if (!require("skimr")) install.packages("skimr")
library("skimr")

@@

plt <- sal_median %>%
  ggplot(aes(
    x = montht,
    y = as.factor(depth),
    fill = median(sal_insitu_ctd)
  ), color = "white") +
  geom_tile() +
  scale_fill_gradientn(colors = viridis(5), breaks = seq(31, 36, by = 1), na.value = "grey") +
  labs(x = "", y = "", fill = "Salinity") +
  scale_x_discrete(position = "top") +
  scale_y_discrete(name = "", limits = rev(levels(as.factor(tmp$depth)))) +
  # scale_y_discrete(name = "", limits = rev(levels(as.factor(tmp$depth))),
  #                  rev(levels(tmp$depth))[c(1,3,5,7,9)]) +
  # coord_equal() +
  theme(legend.position = "top",
        axis.text.y = element_text(size = 13),
        axis.text.x = element_text(size = 13),
        legend.text = element_text(size = 13),
        legend.title = element_text(size = 14),
        #legend.key.size = unit(1.5, "cm"),
        legend.key.height = unit(0.8, "cm"),
        legend.key.width  = unit(2, "cm"))
#plt
